Modelling the City of Melbourne Pedestrian Data

### 2017-05-07 presentation/proposal_pres.Rmd
fixed diagram of sensors, alpha = 1 in geom_path plot of daily patterns

# How is the data collected?

@@

_source: http://www.pedestrian.melbourne.vic.gov.au/pdf/CityofMelbournePedestrianCountingSystem.pdf _

@@

#### For example, at Flagstaff Station, we notice a couple of key patterns:
- Weekly cycle
```{r, message= FALSE, warning= FALSE, fig.height = 3, fig.width = 12, echo = FALSE, fig.retina = 2, fig.align= "center"}
bsplot <- ped_df %>% filter(Year == "2016", Month == "June", Mdate < 25, Sensor_ID == "13")
ggplot(bsplot) + geom_line(aes(x = MTime, y = Hourly_Counts)) + ggtitle("Hourly Pedestrian Count at Flagstaff Station", subtitle = "during June 2016") +
      xlab("Hour of the Month") + ylab("Hourly Counts") + theme_light()
```
- Daily sub-cycle
```{r, message= FALSE, warning= FALSE, fig.height=3, echo = FALSE, fig.align= "center", fig.retina = 2}
ggplot(filter(ped_df, Sensor_ID == "13")) + geom_path(aes(x = as.integer(Time), y = Hourly_Counts, colour = Day), alpha = 0.2) +
      xlab("Hour of the Day") + ylab("Hourly Counts") + theme_light()
```

>>>>

## How is the data collected?

@@

_source: http://www.pedestrian.melbourne.vic.gov.au/ _

@@

#### For example, at Flagstaff Station, we notice a couple of key patterns:
- Weekly cycle
```{r, message= FALSE, warning= FALSE, fig.height = 3, fig.width = 12, echo = FALSE, fig.retina = 2, fig.align= "center"}
bsplot <- ped_df %>% filter(Year == "2016", Month == "June", Mdate < 25, Sensor_ID == "13")
ggplot(bsplot) + geom_line(aes(x = MTime, y = Hourly_Counts)) + ggtitle("Hourly Pedestrian Count at Flagstaff Station", subtitle = "during June 2016") +
      xlab("Hour of the Month") + ylab("Hourly Counts") + theme_light()
```
- Daily sub-cycle
```{r, message= FALSE, warning= FALSE, fig.height=3, echo = FALSE, fig.align= "center", fig.retina = 2}
ggplot(filter(ped_df, Sensor_ID == "13")) + geom_path(aes(x = as.integer(Time), y = Hourly_Counts, colour = Day), alpha = 0.2) +
      xlab("Hour of the Day") + ylab("Hourly Counts") + theme_light() +
      guides(colour = guide_legend(override.aes = list(alpha = 1)))
```
